Improvement of crash forces in structures using optimization tools.

### 2016-07-28 paper.tex

\documentclass[cmfonts]{witpress}
\usepackage{todonotes}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{amssymb}
\usepackage{subcaption}
\captionsetup{compatibility=false}
% \usepackage{natbib}
\bibliographystyle{witpress}

@@

\section{Conclusions}
\todo{Quitar el usepackage todonotes}
\section{Acknowledgments}

>>>>

\documentclass[cmfonts]{witpress}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{amssymb}
\usepackage{subcaption}
\captionsetup{compatibility=false}
% \usepackage{natbib}
\bibliographystyle{witpress}

@@

\section{Conclusions}
From this research the following conclusions can be drawn:
\begin{itemize}
	\item The crash behavior of adhesively bonded steel crash boxes have been successfully simulated in a commercial finite element package. Results have been validated with experimental data in the literature.
	\item A description of a suitable optimization method for the analyzed crash boxes is provided. A multiobjective algorithm enables the balancing of contrasting objective functions like the specific energy absorption and the peak loads of the structures.
\end{itemize}

\section{Acknowledgments}
The research leading to these results has received funding from the Spanish Government (Ministerio de Economía y Competitividad) under grant agreement DPI2013-41893-R. The authors fully acknowledge the support received.
